Biologically-Constrained Region Merging for Connectome Reconstruction

### 2018-03-14 papers/eccv2018/0_introduction.tex
add intro: biological constraints

The field of connectomics considers the problem of reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}. 
%Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
%It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transforms to generate initial over-segmentation, followed by region merging steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
For region merging, most methods do not use prior biological knowledge of the 3D shape of neural structures.

@@

We can make use of both geometric and topological prior information to produce more accurate reconstructions matching the underlying biology (Fig.~\ref{fig:teaser_pipeline}).

>>>>

The field of connectomics considers the problem of reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}. 
%Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
%It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transforms to generate initial over-segmentation, followed by region merging steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
%For region merging, most methods do not use prior biological knowledge of the 3D shape of neural structures.

@@

Due to their biological nature, these over-segmented regions are connected with specific geomtric and topological properties. For example, L-shape juctions and Arrow-shape junctions are rare in neural structures and these regions do not form cycles. Thus, we can make use and learn these shape prior information to produce more accurate region merging to match the underlying biology (Fig.~\ref{fig:teaser_pipeline}).
